Title of the paper

### 2024-12-01 paper.tex
Added sections and prompts

\author{%
  Nikolaj Banke Jensen \\ %\thanks{Use footnote for providing further information about author (webpage, alternative address)---\emph{not} for acknowledging funding agencies.}
  Department of Computer Science\\
  University of Oxford\\
  \texttt{nikolaj.jensen@cs.ox.ac.uk} \\
  % examples of more authors
  \And
  Jamie Vicary \\
  Department of Computer Science and Technology \\
  University of Cambridge \\
  \texttt{jamie.vicary@cl.cam.ac.uk} \\
  % \AND
  % Coauthor \\
  % Affiliation \\
  % Address \\
  % \texttt{email} \\
  % \And
  % Coauthor \\
  % Affiliation \\
  % Address \\
  % \texttt{email} \\
  % \And
  % Coauthor \\
  % Affiliation \\
  % Address \\
  % \texttt{email} \\
}

@@

\section{Introduction}
Hello world
\section{Related Work}
\section{Method}
\section{Experimental Results}
\subsection{Generative Networks}
\section{Conclusion}

>>>>

\author{%
  Nikolaj Banke Jensen \\ %\thanks{Use footnote for providing further information about author (webpage, alternative address)---\emph{not} for acknowledging funding agencies.}
  Department of Computer Science\\
  University of Oxford\\
  \texttt{nikolaj.jensen@cs.ox.ac.uk} \\
  \And
  Jamie Vicary \\
  Department of Computer Science and Technology \\
  University of Cambridge \\
  \texttt{jamie.vicary@cl.cam.ac.uk} \\
}

@@

\section{Introduction}
\textit{Introduce the idea of idempotent neural networks; give the definition. Justification for usefulness in applications where solutions can be both idempotent and not, and where the idempotent solution may be beneficial. Give a brief overview of the rest of the paper.}

\section{Method}
\textit{Outline the perturbation analysis which yielded the update rule. Jordan Normal form justification for looking at eigenvalues and for fixed-points. Stability analysis (and nice Julia heatmap) to argue that specific fixed-points are reached. Compare ordinary and modified autodiff by looking at derivative on a single-layer, non-bias network.}

\section{Experimental Results}
\textit{On experimental networks we give line graphs comparing absolute error at varying learning rates. We also give line graphs for LRs over many epochs. Takeaway message is that for deeper/wider networks we outperform ordinary autodiff by a lot.}

\textit{We replicate the results of IGN on MNIST and CelebA. Latent space analysis. Takeaway is that we show application to a U-net GAN architecture based on Conv layers.}

\section{Related Work}
\textit{Review Idempotent Generative Networks, contrasting our work on a gradient-free approach. Have others applied perturbation theory to ML? We suffer same problems as GANs: mode collapse.}

\section{Conclusion}
\textit{Give a conclusion of central idea: the use of perturbation analysis to find an iterator which we have successfully applied to a range of toy examples and GAN scenarios.}
